Concurrent, Parallel Garbage Collection in Linear Time

### 2016-05-27 finaletd/mainabstract.tex
abstract correcteds

Concurrent programming is used in shared memory and distributed memory systems. State of the art shared memory systems uses a single concurrent garbage collector thread that processes the reference graph. A single concurrent garbage collector does not utilize multiple compute resources. Distributed memory systems have very few complete garbage collection algorithms but use global barriers, centralized and does not scale well. This thesis  focuses on designing garbage collection algorithms for shared memory and distributed memory systems that satisfy the following properties: concurrent, parallel, scalable, localized (decentralized), low pause time, high promptness, no global synchronization, safe, complete, and operates in linear time.

>>>>

Concurrent programming is used in shared memory and distributed memory systems. State of the art shared memory systems use a single concurrent garbage collector thread that processes the reference graph. Distributed memory systems have very few complete garbage collection algorithms and those that exists use global barriers, centralized and do not scale well. This thesis  focuses on designing garbage collection algorithms for shared memory and distributed memory systems that satisfy the following properties: concurrent, parallel, scalable, localized (decentralized), low pause time, high promptness, no global synchronization, safe, complete, and operates in linear time.
